Correctly Optimizing Abstract Abstract Machines

### 2013-04-02 paper/paper.tex
Use k for continuation addresses.
Conflicts:

	paper/paper.tex

\begin{figure}
\begin{gather*}
\begin{align*}
\traces(\mexp) &= \{ \ev[^{\mtcntr}]{\mexp,\varnothing,\varnothing,\kmt} \multimachstep \mstate \} \text{ where }
\end{align*}
\\[2mm]
\begin{array}{@{}r@{\ }c@{\ }l@{}}
\mstate &\machstep&\mstate' \text{ defined to be the following} \\
&&\text{let } \mcntr' =\tick(\mstate) \\
%% EVAL
\ev{\svar\mvar,\menv,\msto,\mkont} &\machstep&
\co{\mkont,\mval,\msto}
\text{ if }\mval \in \msto(\menv(\mvar))
\\
\ev{\slit\mlit,\menv,\msto,\mkont} &\machstep&
\co{\mkont,\mlit,\msto}
\\
\ev[^\mcntr]{\slam\mvar\mexp,\menv,\msto,\mkont} &\machstep&
\co[^{\mcntr'}]{\mkont,\clos{\mvar,\mexp,\menv},\msto}
\\
\ev[^\mcntr]{\sapp[^\mlab]{\mexpi0}{\mexpi1},\menv,\msto,\mkont} &\machstep&
\ev[^{\mcntr'}]{\mexpi{0},\menv,\msto',\kar[_\mlab^\mcntr]{\mexpi{1},\menv,\maddr}}
\\
&&
\text{ where }\maddr = \allockont^\mcntr_\mlab(\msto,\mkont) \\
&&\phantom{\text{ where }}\msto' = \msto\sqcup[\maddr \mapsto \setof{\mkont}]
\\
\ev[^\mcntr]{\sif[^\mlab]{\mexpi0}{\mexpi1}{\mexpi2},\menv,\msto,\mkont} &\machstep&
\ev[^{\mcntr'}]{\mexpi0,\menv,\msto',\kif[^\mcntr]{\mexpi1,\mexpi2,\menv,\maddr}}
\\
&&
\text{ where }\maddr = \allockont^\mcntr_\mlab(\msto,\mkont) \\
&&\phantom{\text{ where }}\msto' = \msto\sqcup[\maddr \mapsto \setof{\mkont}]
\\[2mm]
%% CONTINUE
\co{\kmt,\mval,\msto} &\machstep&
\ans{\msto,\mval}
\\
\co{\kar[^\mcntr_\mlab]{\mexp,\menv,\maddr_\mkont},\mval,\msto} & \machstep&
\ev[^\mcntr]{\mexp,\menv,\msto,\kfn[^\mcntr_\mlab]{\mval,\maddr_\mkont}}
\\
\co{\kfn[^\mcntr_\mlab]{{\mvalx{u}},\maddr_\mkont},\mval,\msto} & \machstep&
\ap[^\mcntr_\mlab]{\mvalx{u},\mval,\mkont,\msto}
\text{ if }\mkont \in \msto(\maddr_\mkont)
\\
\co{\kif[^\mcntr]{\mexpi0,\mexpi1,\menv,\maddr_\mkont},\strue,\msto} & \machstep&
\ev[^{\mcntr'}]{\mexpi0,\menv,\msto,\mkont}
\text{ if }\mkont\in\msto(\maddr_\mkont)
\\
\co{\kif[^\mcntr]{\mexpi0,\mexpi1,\menv,\maddr_\mkont},\sfalse,\msto} & \machstep&
\ev[^{\mcntr'}]{\mexpi1,\menv,\msto,\mkont}
\text{ if }\mkont\in\msto(\maddr_\mkont)
\\[2mm]
%% APPLY
\ap[^\mcntr_\mlab]{\clos{\mvar,\mexp,\menv},\mval,\msto,\mkont} & \machstep&
\ev[^{\mcntr'}\!]{\mexp,\menv',\msto',\mkont}
\\
&&\text{ where } \maddr  =\alloc(\mstate) \\
&&\phantom{\text{ where }} \menv' = \menv[\mvar\mapsto\maddr] \\
&&\phantom{\text{ where }} \msto' = \msto\sqcup[\maddr\mapsto\{\mval\}] \\
\\
\ap[^\mcntr_\mlab]{\mop,\mval,\msto,\mkont} & \machstep&
\co{\mkont,\mval',\msto}
\text{ if } \mval'\in\interpdelta(\mop,\mval)
\end{array}
\end{gather*}
\caption{Abstract abstract machine for ISWIM}
\label{fig:aam}
\end{figure}

\paragraph{Concrete interpretation} To characterize concrete interpretation, set the implicit
parameters of the relation given in figure~\ref{fig:aam} as follows:
\begin{align*}
\alloc(\mstate) &= \maddr \mbox{ where } \maddr \notin \mstate.\msto \\
\allockont^\mcntr_\mlab(\msto,\mkont) \mbox{ where } \maddr \notin \msto
\end{align*}
where $\sqcup$ on stores is a point-wise lifting of $\sqcup$, \ie, $\msto
\sqcup \msto' = \lambda \maddr. \msto(\maddr) \sqcup
\msto'(\maddr)$. These functions appear to ignore $\mlab$ and
$\mcntr$, but they can be used to determinize the choice of fresh
addresses.  The resulting relation is non-deterministic in its choice
of addresses, however it must always choose a fresh address when
allocating a continuation or variable binding.  If we consider machine
states equivalent up to consistent renaming and fix an allocation
scheme, this relation defines a deterministic machine (the relation is
really a function).

@@

The uniform $k$-CFA allocation strategy would make $\traces$ in figure
\ref{fig:aam} a computable abstraction of possible executions, but not an
efficient one.  Through
this section, we explain a succession of approximations
to reach the baseline analysis.  At each stage, we measure performance to
identify the importance of each choice.
%
We ground this path by first formulating the analysis in terms of a classic
fixed-point computation.

@@

In the next subsection, we fix this with store widening and reach a polynomial
(albeit of high degree) complexity.
%
This widening effectively lifts the store out of individual states to create
a single, global shared store for all.

@@

To achieve this linearity for continuations, we allocate an address
for the value position when we create the continuation.  This address
and the tail address are both determined by the label of the
application point, so the space becomes linear and the overall
complexity drops to cubic.  This is a critical abstraction in
languages with $n$-ary functions, since otherwise the continuation
space grows super-exponentially. We extend the semantics to
additionally allocate an address for the function value when creating
the $\kfn{}$ continuation. The continuation has to store this address
to remember where to retreive values from in the store, though some allocation
strategies allow this representation to be ellided.

@@

\begin{figure}
\begin{align*}
\compile{\_} &: \Expr \to \Store \\
             &\phantom{: \Expr } \to \Env  \times \StoreDelta \times \Kont \times \Counter \\
             &\phantom{: \Expr } \to \State \\
\mcntr' &= \tick(\mlab,\menv,\msto,\mcntr) \\
\compile{\svar\mvar}_\msto &=
 \lambda^\mcntr(\menv,\msdiff,\mkont) .
\spchoice
{\co{\mkont,\saddr{\menv(\mvar)}},\msdiff}
{\co{\mkont,\superposition{\msto(\menv(\mvar))}},\msdiff}
\\
\compile{\slit\mlit}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\co{\mkont,\mlit},\msdiff
\\
\compile{\slam\mvar\mexp}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\co{\mkont,\clos{\mvar,\compile{\mexp},\menv}},\msdiff
\\
\compile{\sapp[^\mlab]{\mexpi0}{\mexpi1}}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\compile{\mexpi0}^{\mcntr'}(\menv,\msdiff',\kar[_\mlab^\mcntr]{\compile{\mexpi1},\menv,\maddr_\mkont})
\\
&\setlength\arraycolsep{5pt}
\begin{array}{lrl}
\text{ where } & \maddr_\mkont = \allockont^\mcntr_\mlab(\msto,\mkont) \\
               & \msdiff' = \cons{\ttuple{\maddr_\mkont}{\setof{\mkont}}}{\msdiff}
\end{array}
\\
\compile{\sif[^\mlab]{\mexpi0}{\mexpi1}{\mexpi2}}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\compile{\mexpi0}^{\mcntr'}(\menv,\msdiff',\kif[^\mcntr]{\compile{\mexpi1},\compile{\mexpi2},\menv,\maddr})
\\
&\text{ where }\maddr_\mkont = \allockont^\mcntr_\mlab(\msto,\mkont) \\
&\phantom{\text{ where }} \msdiff' = \cons{\ttuple{\maddr_\mkont}{\setof{\mkont}}}{\msdiff}
\end{align*}
\caption{Abstract compilation}
\label{fig:compile}
\end{figure}

\begin{figure}
\begin{gather*}
\begin{align*}
\traces(\mexp) &= \setof{ \inject(\compile{\mexp}^\mtcntr_\bot(\bot,\epsilon,\kmt)) \multimachstep \mstate}
                    \text{ where } \\
\inject(\mastate,\msdiff) &= \wn(\mastate,\replay(\msdiff,\bot)) \\
\wn(\mastate,\msto) \machstep \wn(\mastate',\msto') &\iff \mastate \cmachstep_\msto \mastate',\msdiff \\
\msdiff \text{ is such that } &\replay(\msdiff,\msto) = \msto'
\end{align*}
\\[2mm]
\begin{align*}
%% CONTINUE
\co{\kmt,\mval} &\cmachstep_\msto
\ans{\mval'},\epsilon \text{ if } \mval' \in \spchoice{\force(\msto,\mval)}{\force(\mval)}
\\
\co{\kar[^\mcntr_\mlab]{\mcomp,\menv,\maddr_\mkont},\mval} & \cmachstep_\msto
\mcomp^\mcntr(\msto)(\menv,\msdiff,\kfn[^\mcntr_\mlab]{\maddr_f,\maddr_\mkont}) \\
\text{ where } \maddr_f &= \alloc(\mstate) \\
               \msdiff &= \cons{\ttuple{\maddr_f}{\force(\msto,\mval)}}{\epsilon}
\\
\co{\kfn[^\mcntr_\mlab]{\maddr_f,\maddr_\mkont},\mval} & \cmachstep_\msto
\ap[^\mcntr_\mlab]{\mval,\mval\mkont},\epsilon \\
\text{ if }\mval &\in \msto(\maddr_f), \mkont \in \msto(\maddr_\mkont)
\\
\co{\kif[^\mcntr]{\mcompi0,\mcompi1,\menv,\maddr},\strue} & \cmachstep_\msto
\mcompi{0}^\mcntr(\msto)(\menv,\epsilon,\mkont)
\text{ if }\mkont\in\msto(\maddr)
\\
\co{\kif[^\mcntr]{\mcompi0,\mcompi1,\menv,\maddr},\sfalse} & \cmachstep_\msto
\mcompi{1}^\mcntr(\msto)(\menv,\epsilon,\mkont)
\text{ if }\mkont\in\msto(\maddr)
\\[2mm]
%% APPLY
\ap[^\mcntr_\mlab]{\clos{\mvar,\mcomp,\menv},\mval,\mkont} & \cmachstep_\msto
\mcomp^{\mcntr'}(\msto)(\menv',\msdiff,\mkont) \\
\text{ where }\menv' &= \menv[\mvar\mapsto\maddr] \\
              \msdiff &= \cons{\ttuple{\maddr}{\force(\msto,\mval)}}{\epsilon}
\\
\ap{\mop,\mval,\mkont} & \cmachstep_\msto
\co{\mkont,\mval'},\epsilon \\
\text{ where } \mvalx{u} &\in \spchoice{\force(\msto,\mval)}{\force(\mval)}, \mval'\in\interpdelta(\mop,\mvalx{u})
\end{align*}
\end{gather*}
\caption{Abstract abstract machine for compiled ISWIM}
\label{fig:caam}
\end{figure}

\paragraph{Correctness}
The correctness of abstract compilation seems obvious, but it has
never before been rigorously proved. What constitutes correctness in
the case of dropped states, anyway? Applying an abstract bytecode's
function does many ``steps'' in one go, at the end of which, the two
semantics line up again (modulo representation of expressions). This
constitutes the use of a notion of stuttering. We provide a formal
analysis of abstract compilation \emph{without} store widening with a proof
of a stuttering bisimulation~\cite{ianjohnson:BCG88} between this
semantics and lazy non-determinism without widening to show precision
preservation. We revisit store widening at the end of the section.

>>>>

\begin{figure}
\begin{gather*}
\begin{align*}
\traces(\mexp) &= \{ \ev[^{\mtcntr}]{\mexp,\varnothing,\varnothing,\kmt} \multimachstep \mstate \} \text{ where }
\end{align*}
\\[2mm]
\begin{array}{@{}r@{\ }c@{\ }l@{}}
\mstate &\machstep&\mstate' \text{ defined to be the following} \\
&&\text{let } \mcntr' =\tick(\mstate) \\
%% EVAL
\ev{\svar\mvar,\menv,\msto,\mkont} &\machstep&
\co{\mkont,\mval,\msto}
\text{ if }\mval \in \msto(\menv(\mvar))
\\
\ev{\slit\mlit,\menv,\msto,\mkont} &\machstep&
\co{\mkont,\mlit,\msto}
\\
\ev[^\mcntr]{\slam\mvar\mexp,\menv,\msto,\mkont} &\machstep&
\co[^{\mcntr'}]{\mkont,\clos{\mvar,\mexp,\menv},\msto}
\\
\ev[^\mcntr]{\sapp[^\mlab]{\mexpi0}{\mexpi1},\menv,\msto,\mkont} &\machstep&
\ev[^{\mcntr'}]{\mexpi{0},\menv,\msto',\kar[_\mlab^\mcntr]{\mexpi{1},\menv,\mkaddr}}
\\
&&
\text{ where }\mkaddr = \allockont^\mcntr_\mlab(\msto,\mkont) \\
&&\phantom{\text{ where }}\msto' = \msto\sqcup[\mkaddr \mapsto \setof{\mkont}]
\\
\ev[^\mcntr]{\sif[^\mlab]{\mexpi0}{\mexpi1}{\mexpi2},\menv,\msto,\mkont} &\machstep&
\ev[^{\mcntr'}]{\mexpi0,\menv,\msto',\kif[^\mcntr]{\mexpi1,\mexpi2,\menv,\mkaddr}}
\\
&&
\text{ where }\mkaddr = \allockont^\mcntr_\mlab(\msto,\mkont) \\
&&\phantom{\text{ where }}\msto' = \msto\sqcup[\mkaddr \mapsto \setof{\mkont}]
\\[2mm]
%% CONTINUE
\co{\kmt,\mval,\msto} &\machstep&
\ans{\msto,\mval}
\\
\co{\kar[^\mcntr_\mlab]{\mexp,\menv,\mkaddr},\mval,\msto} & \machstep&
\ev[^\mcntr]{\mexp,\menv,\msto,\kfn[^\mcntr_\mlab]{\mval,\mkaddr}}
\\
\co{\kfn[^\mcntr_\mlab]{{\mvalx{u}},\mkaddr},\mval,\msto} & \machstep&
\ap[^\mcntr_\mlab]{\mvalx{u},\mval,\mkont,\msto}
\text{ if }\mkont \in \msto(\mkaddr)
\\
\co{\kif[^\mcntr]{\mexpi0,\mexpi1,\menv,\mkaddr},\strue,\msto} & \machstep&
\ev[^{\mcntr'}]{\mexpi0,\menv,\msto,\mkont}
\text{ if }\mkont\in\msto(\mkaddr)
\\
\co{\kif[^\mcntr]{\mexpi0,\mexpi1,\menv,\mkaddr},\sfalse,\msto} & \machstep&
\ev[^{\mcntr'}]{\mexpi1,\menv,\msto,\mkont}
\text{ if }\mkont\in\msto(\mkaddr)
\\[2mm]
%% APPLY
\ap[^\mcntr_\mlab]{\clos{\mvar,\mexp,\menv},\mval,\msto,\mkont} & \machstep&
\ev[^{\mcntr'}\!]{\mexp,\menv',\msto',\mkont}
\\
&&\text{ where } \maddr  =\alloc(\mstate) \\
&&\phantom{\text{ where }} \menv' = \menv[\mvar\mapsto\maddr] \\
&&\phantom{\text{ where }} \msto' = \msto\sqcup[\maddr\mapsto\{\mval\}] \\
\\
\ap[^\mcntr_\mlab]{\mop,\mval,\msto,\mkont} & \machstep&
\co{\mkont,\mval',\msto}
\text{ if } \mval'\in\interpdelta(\mop,\mval)
\end{array}
\end{gather*}
\caption{Abstract abstract machine for ISWIM}
\label{fig:aam}
\end{figure}

\paragraph{Concrete interpretation} To characterize concrete interpretation, set the implicit
parameters of the relation given in figure~\ref{fig:aam} as follows:
\begin{align*}
\alloc(\mstate) &= \maddr \mbox{ where } \maddr \notin \text{ the } \msto \text{ within } \mstate \\
\allockont^\mcntr_\mlab(\msto,\mkont) &=\mkaddr \mbox{ where } \mkaddr \notin \msto
\end{align*}
These functions appear to ignore $\mlab$ and $\mcntr$, but they can be
used to determinize the choice of fresh addresses. The $\sqcup$ on
stores in the figure is a point-wise lifting of $\cup$: $\msto \sqcup \msto' =
\lambda \maddr. \msto(\maddr) \cup \msto'(\maddr)$. The resulting
relation is non-deterministic in its choice of addresses, however it
must always choose a fresh address when allocating a continuation or
variable binding.  If we consider machine states equivalent up to
consistent renaming and fix an allocation scheme, this relation
defines a deterministic machine (the relation is really a function).

@@

The uniform $k$-CFA allocation strategy would make $\traces$ in figure
\ref{fig:aam} a computable abstraction of possible executions, but one
that is too inefficient to run, even on small examples.  Through this
section, we explain a succession of approximations to reach a more
appropriate baseline analysis.
%
We ground this path by first formulating the analysis in terms of a
classic fixed-point computation.

@@

In the next subsection, we fix this with store widening to reach polynomial
(albeit of high degree) complexity.
%
This widening effectively lifts the store out of individual states to create
a single, global shared store for all.

@@

To achieve this linearity for continuations, we allocate an address
for the value position when we create the continuation.  This address
and the tail address are both determined by the label of the
application point, so the space becomes linear and the overall
complexity drops to cubic.  This is a critical abstraction in
languages with $n$-ary functions, since otherwise the continuation
space grows super-exponentially. We extend the semantics to
additionally allocate an address for the function value when creating
the $\kfn{}$ continuation. The continuation has to contain this address
to remember where to retreive values from in the store.

@@

\begin{figure}
\begin{align*}
\compile{\_} &: \Expr \to \Store \\
             &\phantom{: \Expr } \to \Env  \times \StoreDelta \times \Kont \times \Counter \\
             &\phantom{: \Expr } \to \State \\
\mcntr' &= \tick(\mlab,\menv,\msto,\mcntr) \\
\compile{\svar\mvar}_\msto &=
 \lambda^\mcntr(\menv,\msdiff,\mkont) .
\spchoice
{\co{\mkont,\saddr{\menv(\mvar)}},\msdiff}
{\co{\mkont,\superposition{\msto(\menv(\mvar))}},\msdiff}
\\
\compile{\slit\mlit}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\co{\mkont,\mlit},\msdiff
\\
\compile{\slam\mvar\mexp}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\co{\mkont,\clos{\mvar,\compile{\mexp},\menv}},\msdiff
\\
\compile{\sapp[^\mlab]{\mexpi0}{\mexpi1}}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\compile{\mexpi0}^{\mcntr'}(\menv,\msdiff',\kar[_\mlab^\mcntr]{\compile{\mexpi1},\menv,\mkaddr})
\\
&\setlength\arraycolsep{5pt}
\begin{array}{lrl}
\text{ where } & \mkaddr = \allockont^\mcntr_\mlab(\msto,\mkont) \\
               & \msdiff' = \cons{\ttuple{\mkaddr}{\setof{\mkont}}}{\msdiff}
\end{array}
\\
\compile{\sif[^\mlab]{\mexpi0}{\mexpi1}{\mexpi2}}_\msto &= \lambda^\mcntr(\menv,\msdiff,\mkont) .
\compile{\mexpi0}^{\mcntr'}(\menv,\msdiff',\kif[^\mcntr]{\compile{\mexpi1},\compile{\mexpi2},\menv,\maddr})
\\
&\text{ where }\mkaddr = \allockont^\mcntr_\mlab(\msto,\mkont) \\
&\phantom{\text{ where }} \msdiff' = \cons{\ttuple{\mkaddr}{\setof{\mkont}}}{\msdiff}
\end{align*}
\caption{Abstract compilation}
\label{fig:compile}
\end{figure}

\begin{figure}
\begin{gather*}
\begin{align*}
\traces(\mexp) &= \setof{ \inject(\compile{\mexp}^\mtcntr_\bot(\bot,\epsilon,\kmt)) \multimachstep \mstate}
                    \text{ where } \\
\inject(\mastate,\msdiff) &= \wn(\mastate,\replay(\msdiff,\bot)) \\
\wn(\mastate,\msto) \machstep \wn(\mastate',\msto') &\iff \mastate \cmachstep_\msto \mastate',\msdiff \\
\msdiff \text{ is such that } &\replay(\msdiff,\msto) = \msto'
\end{align*}
\\[2mm]
\begin{align*}
%% CONTINUE
\co{\kmt,\mval} &\cmachstep_\msto
\ans{\mval'},\epsilon \text{ if } \mval' \in \spchoice{\force(\msto,\mval)}{\force(\mval)}
\\
\co{\kar[^\mcntr_\mlab]{\mcomp,\menv,\mkaddr},\mval} & \cmachstep_\msto
\mcomp^\mcntr(\msto)(\menv,\msdiff,\kfn[^\mcntr_\mlab]{\maddr_f,\mkaddr}) \\
\text{ where } \maddr_f &= \alloc(\mstate) \\
               \msdiff &= \cons{\ttuple{\maddr_f}{\force(\msto,\mval)}}{\epsilon}
\\
\co{\kfn[^\mcntr_\mlab]{\maddr_f,\mkaddr},\mval} & \cmachstep_\msto
\ap[^\mcntr_\mlab]{\mval,\mval\mkont},\epsilon \\
\text{ if }\mval &\in \msto(\maddr_f), \mkont \in \msto(\mkaddr)
\\
\co{\kif[^\mcntr]{\mcompi0,\mcompi1,\menv,\maddr},\strue} & \cmachstep_\msto
\mcompi{0}^\mcntr(\msto)(\menv,\epsilon,\mkont)
\text{ if }\mkont\in\msto(\maddr)
\\
\co{\kif[^\mcntr]{\mcompi0,\mcompi1,\menv,\maddr},\sfalse} & \cmachstep_\msto
\mcompi{1}^\mcntr(\msto)(\menv,\epsilon,\mkont)
\text{ if }\mkont\in\msto(\maddr)
\\[2mm]
%% APPLY
\ap[^\mcntr_\mlab]{\clos{\mvar,\mcomp,\menv},\mval,\mkont} & \cmachstep_\msto
\mcomp^{\mcntr'}(\msto)(\menv',\msdiff,\mkont) \\
\text{ where }\menv' &= \menv[\mvar\mapsto\maddr] \\
              \msdiff &= \cons{\ttuple{\maddr}{\force(\msto,\mval)}}{\epsilon}
\\
\ap{\mop,\mval,\mkont} & \cmachstep_\msto
\co{\mkont,\mval'},\epsilon \\
\text{ where } \mvalx{u} &\in \spchoice{\force(\msto,\mval)}{\force(\mval)}, \mval'\in\interpdelta(\mop,\mvalx{u})
\end{align*}
\end{gather*}
\caption{Abstract abstract machine for compiled ISWIM}
\label{fig:caam}
\end{figure}

\paragraph{Correctness}
The correctness of abstract compilation seems obvious, but it has
never before been rigorously proved. What constitutes correctness in
the case of dropped states, anyway? Applying an abstract bytecode's
function does many ``steps'' in one go, at the end of which, the two
semantics line up again (modulo representation of expressions). This
constitutes the use of a notion of stuttering. We provide a formal
analysis of abstract compilation \emph{without} store widening with a proof
of a stuttering bisimulation~\cite{ianjohnson:BCG88} between this
semantics and lazy non-determinism without widening to show precision
preservation. %We revisit store widening at the end of the section.
